Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-04 inc/hardware/magnetic_lenses/maglens.tex
merge more comments on magentic lens design

El-Kareh and El-Kareh provide an analysis for symmetric lenses with magnetic shielding and a pole-piece (see Ref. \cite{el-kareh_electron_1970} chapter 8, with the most useful information being in section 8.7).
They define two parameters,
\begin{equation}
  k^2 \equiv \frac{e}{8 m V_r} B_0^2 R^2
\end{equation}
and
\begin{equation} \label{eq:elkareh_k2}
  \beta \equiv k^2 V_r / (NI)^2 \,\text{,}
\end{equation}
where $N$ is the number of loops, $I$ is the current in a single loop, $B_0$ is the maximum axial magnetic field strength, $R$ is the bore radius and $V_r$ is the relativity corrected acceleration potential, given by
\begin{equation}
  V_r = V ( 1 + \frac{0.978 \cdot 10^{-6}}{\text{Volt}} V ) \,\text{.}
\end{equation}
They then derive a number of formulae and tabulate the results for a variety of parameters.
Using these tabulated results, and for a choice of parameters one can determine the number of ampere-turns ($NI$) to create a certain focal length.

Since the drift tube has an outer diameter $D=$0.5in and the pole-piece gap length is $S$=0.1in, the lens has a ratio $S/D=0.2$.
By their table 8.2a this results in $\beta=0.0146$. Then, to create a focal length of 4in ($f/R=16$) table 8.13 gives a value for $k^2 \approx 0.06$.
Finally substituting this value into \ref{eq:elkareh_k2}, with $V=30$kV ($V_r\approx30.88$kV), one can deduce that $NI\approx356$A.

>>>>

El-Kareh and El-Kareh provide an analysis for symmetric lenses with magnetic shielding and a pole-piece (see Ref. \cite{el-kareh_electron_1970} chapter 8, with the most useful information being in section 8.7).
They define two parameters,
\begin{equation}
  k^2 \equiv \frac{e}{8 m V_r} B_0^2 R^2
\end{equation}
and
\begin{equation} \label{eq:elkareh_k2}
  \beta \equiv k^2 V_r / (NI)^2 \,\text{,}
\end{equation}
where $N$ is the number of loops, $I$ is the current in a single loop, $B_0$ is the maximum axial magnetic field strength, $R$ is the bore radius and $V_r$ is the relativity corrected acceleration potential, given by
\begin{equation}
  V_r = V ( 1 + \frac{0.978 \cdot 10^{-6}}{\text{Volt}} V ) \,\text{.}
\end{equation}
Using the provided tabulated results, and for a choice of parameters one can determine the number of ampere-turns ($NI$) to create a certain focal length.
Since the drift tube has an outer diameter $D=$0.5in and the pole-piece gap length is $S$=0.1in, the lens has a ratio $S/D=0.2$.
By their table 8.2a this results in $\beta=0.0146$.
Then, to create a focal length of 4in ($f/R=16$) table 8.13 in Ref. \cite{el-kareh_electron_1970} gives a value for $k^2 \approx 0.06$.
Finally substituting this value into \ref{eq:elkareh_k2}, with $V=30$kV ($V_r\approx30.88$kV), one can deduce that $NI\approx356$A.
